Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-16 ieee_paper.tex
Updated paper with all figures. Figure 12 is probably not required.

\newfig{figures/source_code.pdf}{6in}{Source code}{fig:source}

@@

\begin{figure*}

  \subfigure[Bandwidth performance under idealized conditions as a
    function of matrix row size. Entries with "cpp" denote cases where
    coding was performed without MIC vector
    instructions.]{\includegraphics[width=.49\linewidth]{figures/test1_readwrite.pdf}\label{fig:band_rw}}
%
  \subfigure[Bandwidth performance under
  idealized conditions as a function of matrix row size. Entries with
  "cpp" denote cases where coding was performed without MIC vector
  instructions.]{\includegraphics[width=.49\linewidth]{figures/test1_gather.pdf}\label{fig:band_gather}}

  \subfigure[Bandwidth performance under idealized conditions as a
    function of matrix row size. Entries with "cpp" denote cases where
    coding was performed without MIC vector instructions. The greater
    speed of the cpp version is obtained throught the use of
    \ttt{\#Ivdep} {\em and\/} \ttt{\_\_assumed\_aligned}. All memory
    is aligned on 64
    bytes.]{\includegraphics[width=.49\linewidth]{figures/test3_gather.pdf}\label{fig:band_gather_ivdep}}
%
  \subfigure[Bandwidth performance on the host under idealized
    conditions as a function of matrix row size. Entries with "cpp"
    denote cases where coding was performed without AVX vector
    instructions. The speed on the CPU matches the speed with AVX
    instructions. All memory is aligned on 32
    bytes.]{\includegraphics[width=.49\linewidth]{figures/host_test1_readwrite_no_temporal_hint.pdf}\label{fig:read_write}}

\caption{Bandwidth Analysis.\todo{not 100\% sure what this plots are.}
  \todo{can we harmozie y-axis?} \todo{ylabel should read "Bandwidth (GB/s)".}
  \todo{remove title.}}

\end{figure*}

@@

\begin{figure*}
  \centering
  \subfigure[Performance of $y=Ax$ on the MIC. Squares: base 1/1 case],
    solid circles: 4/4 case implemented in C++, solid triangles: 4/4
    case implemented with MIC vector instructions. $-O3$ compilation
    options. Each symbol has two cases: with (red) and without blue) 
    with and without Reverse Cuthill-McKee. The grid is $96^3$.}
    {\includegraphics[width=.49\linewidth]{figures/mic_performance_nb_threads.pdf}\label{fig:perf_mic}}
%
  \subfigure[performance on the host on a sparse matrix with $64^3$ rows. Manual
    vectorization brings significant improvement there as
    well.]{\includegraphics[width=.49\linewidth]{figures/64x64x64.pdf}\label{fig:perf_host}}
  \caption{Vectorization matters in practice. Differences in BW
    translate in different performance.\todo{this two plots should ``correlate'' }}
\end{figure*}

\begin{figure*}[t]
  \centering
  \subfigure[Supercompact\todo{is the title? this looks like super compact.}]{\includegraphics[width=.49\linewidth]{figures/supercompact_max_perf.pdf}}
  \subfigure[Compact]{\includegraphics[width=.49\linewidth]{figures/compact_max_perf.pdf}}

  \subfigure[Random]{\includegraphics[width=.49\linewidth]{figures/random_max_perf.pdf}}
  \subfigure[RBF 3D]{\includegraphics[width=.49\linewidth]{figures/rbf_max_perf_run1.pdf}}
  \caption{Performance of "best code" accross instance types. \todo{Why stop at 1.6M
      rows. Is that because of memory limitation? I guess that's what
      it is}\todo{can we remove the title?}\todo{can we harmonize y-axis?}}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/plot_for_natasha_ncar_end_of_year.pdf}

@@

>>>>

\begin{figure*}
  \centering
  %\subfigure[Source code}
  \includegraphics[width=0.8\textwidth]{figures/source_code.pdf}%
  \label{fig:source}
  \caption{Source Code}
\end{figure*}
%\newfig{figures/source_code.pdf}{6in}{Source code}{fig:source}

@@

\begin{figure*}
\centering
  \subfigure[
    Entries with "cpp" denote cases where
    coding was performed without MIC vector
    instructions.]{\includegraphics[width=.40\linewidth]{figures/test1_readwrite.pdf}\label{fig:band_rw}}
%
  \subfigure[ xxx ] 
  {\includegraphics[width=.40\linewidth]{figures/test1_gather.pdf}\label{fig:band_gather}} \\

  \subfigure[The greater
    speed of the cpp version is obtained throught the use of
    \ttt{\#Ivdep} {\em and\/} \ttt{\_\_assumed\_aligned}. All memory
    is aligned on 64
    bytes.]{\includegraphics[width=.40\linewidth]{figures/test3_gather.pdf}\label{fig:band_gather_ivdep}}
%
  \subfigure[
    The speed on the CPU matches the speed with vector instructions.
    All memory is aligned on 32
    bytes.]{\includegraphics[width=.40\linewidth]{figures/host_test1_readwrite_no_temporal_hint.pdf}\label{fig:read_write}}

\caption{Bandwidth performance on the host under idealized conditions as a function of matrix row size.
  Entries with "cpp" denote cases where coding was performed without MIC vector intructions. 
\todo{not 100\% sure what this plots are.}}
\end{figure*}

@@

\begin{figure*}
  \centering
  \subfigure[Performance of $y=Ax$ on the MIC. Squares: base 1/1 case,
    solid circles: 4/4 case implemented in C++, solid triangles: 4/4
    case implemented with MIC vector instructions. $-O3$ compilation
    options. Each symbol has two cases: with (red) and without blue) 
    with and without Reverse Cuthill-McKee. The grid is $96^3$.]
    {\includegraphics[width=.40\linewidth]{figures/mic_performance_nb_threads.pdf}\label{fig:perf_mic}}
%
  \subfigure[Performance on the host on a sparse matrix with $64^3$ rows. Manual
    vectorization brings significant improvement there as
    well.]{\includegraphics[width=.40\linewidth]{figures/64x64x64.pdf}\label{fig:perf_host}}
  \caption{Vectorization matters in practice. Differences in BW
    translate in different performance.\todo{this two plots should ``correlate'' }}
\end{figure*}

\begin{figure}[t]
  \centering
  \subfigure[Supercompact]{\includegraphics[width=.48\linewidth]{figures/supercompact_max_perf.pdf}}
  \subfigure[Compact]{\includegraphics[width=.48\linewidth]{figures/compact_max_perf.pdf}} \\
  \subfigure[Random]{\includegraphics[width=.48\linewidth]{figures/random_max_perf.pdf}}
  \subfigure[RBF 3D]{\includegraphics[width=.48\linewidth]{figures/rbf_max_perf_run1.pdf}}
  \caption{Performance of "best code" accross instance types. \todo{Why stop at 1.6M
      rows. Is that because of memory limitation? I guess that's what
      it is}}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{figures/plot_for_natasha_ncar_end_of_year.pdf}

@@

\begin{figure*}
\centering
\subfigure[No cache effects.]{\includegraphics[width=.33\linewidth]{figures/flops_to_bytes_no_cache-crop.pdf}}%\label{fig:ratio_nocache}}
\subfigure[Best case.]{\includegraphics[width=.33\linewidth]{figures/flops_to_bytes_best-crop.pdf}} %\label{fig:ratio_best}}
\subfigure[worst case.]{\includegraphics[width=.33\linewidth]{figures/flops_to_bytes_worst-crop.pdf}}%\label{fig:ratio_worst}}
\caption{Ratio of flops to bytes; (a) simple count of flops and bytes that require transfer from memory;(b) best and (c) worst
case taking into account that bringing one element of $x$ into memory brings along the remainder of the cache line.}
\label{fig:ratio_bytes_flops}
\end{figure*}
